The 2018 heatwave and its implications on ozone induced damage on vegetation in a subarctic climate

### 2020-10-09 VegOzone.tex
Fix gramma.

Finally, we shall look at the comparison of climatologies derived from observational ozone data and the various reanalysis products (Fig.~\ref{fig:ozone_climatologies}). As representative for the sites, the nearest neighboring grid point has been chosen. The ECMWF products do not reproduce observed surface ozone well. The MACC reanalysis (Fig.~\ref{fig:ozone_climatologies}a) is in general too low ($(9\pm 7)\,\unit{ppb}$) and displays a erroneous seasonal cycle. Ozone concentrations peak already in March followed by a second peak in July. Also CAMSRA matches the observed ozone climatology poorly (Fig.~\ref{fig:ozone_climatologies}b). Despite displaying only one ozone peak, it still does not reproduce the seasonality in northern Fennoscandia well. The CAMSRA spring peak appears to lag behind by $1\,\unit{month}$ and is $5\,\unit{ppb}$ lower, whereas the minimum occurs in January compared to August/September. The annual amplitude ($(26\pm 1)\,\unit{ppb}$) is larger than in the climatology derived from observations ($19\,\unit{ppb}$). Modeled \chem{[O_3]} at Svanvik are even slightly higher than at Pallas. In contrast, the ensemble mean of the Copernicus regional model reanalysis does reproduce the seasonal cycle in northern Fennoscandia quite well (Fig.~\ref{fig:ozone_climatologies}c), but is on average still slightly too low ($(2.8\pm 0.5)\,\unit{ppb}$).

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatologies_portrait}
  \caption{Comparison of climatologies derived from observational data (EBAS, see Fig.~\ref{fig:ozone_climatology_fenoscandic_obs}) with various ozone reanalysis products: (a) ECMWF: MACC reanalysis; (b) ECMWF: CAMS reanalysis; (c) Copernicus: Regional model reanalysis ensemble mean. As representative for the sites, the nearest neighboring grid point has been chosen. The ECMWF products do not reproduce observed surface ozone well. The MACC reanalysis is in general too low and displays a erroneous seasonal cycle. The CAMS reanalysis matches better but does not reproduce the seasonality in northern Fennoscandia. The ensemble mean of the Copernicus regional model reanalysis does reproduce the seasonal cycle in northern Fennoscandia, though the modeled ozone concentrations are slightly too low.}
  \label{fig:ozone_climatologies}
\end{figure}

>>>>

Finally, we shall look at the comparison of climatologies derived from observational ozone data and the various reanalysis products (Fig.~\ref{fig:ozone_climatologies}). As representative for the sites, the nearest neighboring grid point has been chosen. The ECMWF products do not reproduce observed surface ozone well. The MACC reanalysis (Fig.~\ref{fig:ozone_climatologies}a) is in general too low ($(9\pm 7)\,\unit{ppb}$) and displays an erroneous seasonal cycle. Ozone concentrations peak already in March followed by a second peak in July. Also CAMSRA matches the observed ozone climatology poorly (Fig.~\ref{fig:ozone_climatologies}b). Despite displaying only one ozone peak, it still does not reproduce the seasonality in northern Fennoscandia well. The CAMSRA spring peak appears to lag behind by $1\,\unit{month}$ and is $5\,\unit{ppb}$ lower, whereas the minimum occurs in January compared to August/September. The annual amplitude ($(26\pm 1)\,\unit{ppb}$) is larger than in the climatology derived from observations ($19\,\unit{ppb}$). Modeled \chem{[O_3]} at Svanvik are even slightly higher than at Pallas. In contrast, the ensemble mean of the Copernicus regional model reanalysis does reproduce the seasonal cycle in northern Fennoscandia quite well (Fig.~\ref{fig:ozone_climatologies}c), but is on average still slightly too low ($(2.8\pm 0.5)\,\unit{ppb}$).

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatologies_portrait}
  \caption{Comparison of climatologies derived from observational data (EBAS, see Fig.~\ref{fig:ozone_climatology_fenoscandic_obs}) with various ozone reanalysis products: (a) ECMWF: MACC reanalysis; (b) ECMWF: CAMS reanalysis; (c) Copernicus: Regional model reanalysis ensemble mean. As representative for the sites, the nearest neighboring grid point has been chosen. The ECMWF products do not reproduce observed surface ozone well. The MACC reanalysis is in general too low and displays an erroneous seasonal cycle. The CAMS reanalysis matches better but does not reproduce the seasonality in northern Fennoscandia. The ensemble mean of the Copernicus regional model reanalysis does reproduce the seasonal cycle in northern Fennoscandia, though the modeled ozone concentrations are slightly too low.}
  \label{fig:ozone_climatologies}
\end{figure}
